Generalized Tractability

### 2023-06-07 GeneralizedTractability_230529.tex
Updates from Overleaf

\begin{theorem}\label{thm_main_tract2}
Let $T$ be a tractability function as specified in \eqref{eq:Tspec} and satisfying \eqref{eq:Tconditions} and \eqref{eq:ptauassume}.  A problem is $T$-tractable iff there exists $\vp\ge \vzero$ and a positive integer $L_{\vp}$ such that
\begin{equation} \label{eq:tractiff4}
     S_{\vp}:=\sup_{d \in \naturals}
     \sum_{i = \lceil L_{\vp}\, T(0,d,\vp) \rceil}^\infty \frac{1}{T(\lambda^{-1}_{i,d},d,\vp)}< \infty.
\end{equation}

@@

\noindent \textbf{Optimality:}
This proof is similar to the proof for the optimality condition for strong tractability in Theorem \ref{thm_main_strong_tract2}. We must show that $\cp_{\textup{trct}} = \widetilde{\cp}_{\textup{trct}}$.  Then, the expression for  $\cp_{\textup{opt}}$ in this theorem automatically follows from its definition in \eqref{eq:Poptdef}.

@@

\begin{definition}
    A problem is strongly
$T$-tractable with parameter $\vp$ \emph{on the restricted domain $\Omega$} iff the complexity is independent of the dimension of the problem, that is, there exists a positive constant $C_{\vp}$, again independent of $\varepsilon$ and $d$, such that
\begin{equation} \label{eq:rest_strong_tract_def}
	\comp(\varepsilon,d) \le C_{\vp}\, T(\varepsilon^{-1},1,\vp) \qquad \forall(\varepsilon^{-1},d) \in \Omega.
\end{equation}
%\peter{[I am wondering whether this makes sense if $E$ depends on $d$? Do Gnewuch and Wo\'{z}niakowski allow dependence of $E$ on $d$?]}
A problem is 
$T$-tractable with parameter $\vp$ \emph{on the restricted domain $\Omega$} iff the complexity is independent of the dimension of the problem, that is, there exists a positive constant $C_{\vp}$, again independent of $\varepsilon$ and $d$, such that
\begin{equation} \label{eq:rest_tract_def}
	\comp(\varepsilon,d) \le C_{\vp}\, T(\varepsilon^{-1},d,\vp) \qquad \forall(\varepsilon^{-1},d) \in \Omega.
\end{equation}
 Define the closures of the sets of parameters for which our (strong) tractability conditions hold:
\begin{equation*}
	\cp_{\textup{rtrct}} : = \{\vp^* : \eqref{eq:rest_tract_def} \text{ holds }\forall \vp \in (\vp^*,\boldsymbol{\infty})\}, \qquad
	\cp_{\textup{rstrct}} : = \{\vp^* : \eqref{eq:rest_strong_tract_def} \text{ holds }\forall \vp \in (\vp^*,\boldsymbol{\infty})\}.
\end{equation*}
    The  set of optimal parameters is defined as all of those parameters satisfying the (strong) tractability conditions that are not greater than or equal to others:
\begin{gather}
	\label{eq:Poptdef}
	\mathcal{P}_{\textup{ropt}} : = \{\vp^* \in \cp_{\textup{rtrct}} :  \vp^* \notin [\vp,\boldsymbol{\infty}) \ \forall \vp \in  \cp_{\textup{rtrct}} \setminus \{\vp^*\} \}, \\
	\label{eq:Psoptdef}
	\mathcal{P}_{\textup{rsopt}} : = \{\vp^* \in \cp_{\textup{rstrct}} :  \vp^* \notin [\vp,\boldsymbol{\infty}) \ \forall \vp \in  \cp_{\textup{rstrct}} \setminus \{\vp^*\} \}.
\end{gather}
\end{definition}

@@

\item If $M(d) \ge L_{\tau\vp}$ and $E(d) = 0$, then $\{L_{\tau\vp},  \L_{\tau\vp} + 1, \ldots \} \subseteq I_{d,\vp} \setminus \{1\}$.

@@

\bigskip
\noindent \textbf{Optimality:} 
The proof of optimality is analogous to that for Theorem \ref{thm_main_strong_tract2} and is omitted.

@@

\begin{theorem}\label{thm_main_rest_tract}
Let $T$ be a tractability function as specified in \eqref{eq:Tspec} and satisfying \eqref{eq:Tconditions} and \eqref{eq:ptauassume}.  A problem is $T$-tractable on the restricted domain $\Omega$ iff there exists $\vp\ge \vzero$ and a positive integer $L_{\vp}$ such that
\begin{equation} \label{eq:rest_tractiff}
     S_{\vp}:=\sup_{d \in \naturals}
     \sum_{i = \lceil L_{\vp}\, T(0,d,\vp) \rceil}^{M(d)} \frac{1}{T(\lambda^{-1}_{i,d},d,\vp)}< \infty.
\end{equation}
If \eqref{eq:rest_tractiff4} holds for some $\vp$, let $\widetilde{\cp}_{\textup{trct}} : = \{\vp^* : \eqref{eq:tractiff4} \text{ holds }\forall \vp \in (\vp^*,\boldsymbol{\infty}) \}$.
Then $\cp_{\textup{rtrct}} = \widetilde{\cp}_{\textup{rtrct}}$, and the set of optimal  tractability parameters is
\[
\cp_{\textup{ropt}} =
\{\vp^* \in \widetilde{\cp}_{\textup{rtrct}} :  \vp^* \notin [\widetilde{\vp},\boldsymbol{\infty}) \ \forall \widetilde{\vp}\in  \widetilde{\cp}_{\textup{rtrct}} \setminus \{\vp^*\} \}.
\]
\end{theorem}

@@

\noindent \textbf{Necessary condition:}\\
Suppose that we have
$T$-tractability on the restricted domain. That is, for some $\vp \ge \vzero$, there exists a positive constant $C_{\vp}$ such that
\[
\comp(\varepsilon,d)\le C_{\vp}\, T(\varepsilon^{-1},d,\vp) \qquad \forall (\varepsilon^{-1}, d) \in \Omega.
\]
Since the sequence of eigenvalues $\lambda_{1,d}, \lambda_{2,d}, \ldots $ is non-increasing, we have
\begin{equation}\label{eq:lambda_K4}
	\lambda_{\lfloor C_{\vp}\, T(\varepsilon^{-1},d,\vp)\rfloor +1,d}\le \varepsilon \qquad 
 \forall \varepsilon > E(d),\ d \in \naturals.
\end{equation}

For $(\varepsilon^{-1}, d) \in \Omega$, define the positive integers 
\[
i (\varepsilon,d,\vp):= \lfloor C_{\vp}\, T(\varepsilon^{-1},d,\vp)\rfloor +1, \qquad
i (\infty,d,\vp) := \lfloor C_{\vp}\, T(0,d,\vp)\rfloor +1 \ge 1.
\]
It follows by \eqref{eq:lambda_K4} that $\lambda_{i(\varepsilon,d,\vp),d} \le \varepsilon$
for any  $(\varepsilon^{-1}, d) \in \Omega$.
Note furthermore that since $T(\cdot,d,\vp)$ is non-decreasing, we have
\[
i(\varepsilon,d,\vp)\le C_{\vp}\, T(\varepsilon^{-1},d,\vp)+1 \le C_{\vp} T(\lambda_{i(\varepsilon,d,\vp),d}^{-1},d,\vp)+1, \qquad \forall \varepsilon > E(d),\ d \in \naturals.
\]
For $\varepsilon$ taking on all values in $(E(d),\infty)$, $i(\varepsilon,d,\vp)$ takes on (at least) all values in
\[
I_{d,\vp}:=\begin{cases} 
\emptyset, & i(E(d),\vp) = i(\infty,\vp) \\
\{i(\infty,\vp),\ldots, i(E(d),\vp)-1\}, & E(d) > 0, \\
\{i(\infty,\vp), i(\infty,\vp) + 1, \ldots\}, & E(d) = 0.
\end{cases}
\]So,
\[
i\le  C_{\vp} T(\lambda_{i,d}^{-1},d,\vp)+1, \qquad \forall i\in I_{d},  \ d \in \naturals.
\]

This upper bound on $i$ in terms of $T(\lambda_{i,d}^{-1},d,\vp)$ implies via our technical assumption \eqref{eq:ptauassume} that for any $\tau > 1$,
\begin{equation}\label{eq:restrictKfive}
	K_{\vp,\tau}\,T (\lambda_{i,d}^{-1},d,\tau \vp) \ge
	[T(\lambda_{i,d}^{-1},d, \vp)]^\tau
	\ge
	\left[\frac{(i-1)}{C_{\vp}}\right]^\tau \qquad  \forall i\in I_{d},  \ d \in \naturals.
 \end{equation}
To carry the argument further, we need to show that the interval $I_d$ contains the interval
\[
\tI_{d}:=\begin{cases} 
\{i(\infty,d,\vp),\ldots, M(d)\}, & E(d) > 0, \\
\{i(\infty,d,\vp), i(\infty,d,\vp) + 1, \ldots\}, & E(d) = 0.
\end{cases}
\]

Since $I_d = \tI_d$ when $E(d) =0$, we need only consider the case where $E(d) > 0$.  In this case \eqref{eq:Mddef} and \eqref{eq:lambda_K4} imply that
\[
\lambda_{i(E(d),d,\vp),d} \le \lambda_{M(d)+2} \le E(d) < \lambda_{M(d)+1,d}.
\]
This means that $i(E(d),d,\vp)-1 \ge M(d)+1$, and so $I_d \supseteq \tI_d$.

 and this implies
 \[
	 \frac{1}{T (\lambda_{i,d}^{-1},d,\tau \vp)} \le
	\frac{K_{\vp,\tau}\, C_{\vp}^\tau}{(i-1)^\tau}\qquad  \peter{\forall i\in 
 \{i(\infty,d,\vp)+1,\ldots, M(d)\}},  \ d \in \naturals.
\]

Let $\vp' = \tau \vp$. \peter{Like in the proof of Theorem \ref{thm_main_tract2}, we note that $i(\infty,d,\vp) 
\ge i(\infty,d,\vp')$. Furthermore, we also have 
$M(d)\le i(E(d),d,\vp)\le i(E(d),d,\vp')$. Thus,}
summing both sides of the latter inequality over \peter{$\{i(\infty,d,\vp')+1,\ldots, M(d)\} $} it follows that
\begin{equation*}
	\sup_{d\in\naturals} \, \, \sum_{\peter{i=i(\infty,d,\vp')+1}}^{\peter{M(d)}} \frac{1}{T (\lambda_{i,d}^{-1},d,\vp')}
	 \le  K_{\vp,\tau}\, C_{\vp}^\tau
	\sum_{i=2}^{\infty} \frac{1}{(i-1)^\tau} \\
	 \le  K_{\vp,\tau}\, C_{\vp}^\tau
	\zeta (\tau)  < \infty,
\end{equation*}
where $\zeta$ denotes the Riemann zeta function.

\peter{[WHAT REMAINS TO BE DONE (HOPEFULLY NOT HARD): check that the summation range above is not empty.]}

Note now that, for any $d\in\naturals$,
\begin{align*}
 i(\infty,d,\vp') +1  & = \lfloor C_{\vp'}\, T(0,d,\vp')\rfloor +2 \le  \left[C_{\vp'} + \frac{2}{T(0,d,\vp')}   \right]\, T(0,d,\vp')\\
 & \le  \underbrace{\left[C_{\vp'} + \frac{2}{T(0,1,\vp')}   \right]}_{=:L_{\vp'}}\, T(0,d,\vp')
 \le \lceil L_{\vp'} T(0,d,\vp')\rceil .
\end{align*}
For this choice of $L_{\vp'}$ we have
\[
\sup_{d\in\naturals}\,\, \sum_{i=\lceil L(\vp') T(0,d,\vp')\rceil}^{\peter{M(d)}} \frac{1}{T(\lambda_{i,d}^{-1},d, \vp')}
\le
\sup_{d\in\naturals} \, \, \sum_{i=i (\infty,d,\vp')+1}^\infty \frac{1}{T (\lambda_{i,d}^{-1},d,\vp')} <
\infty.
\]
This yields \eqref{eq:tractiff4} with $\vp$ replaced by $\vp'$, so we see the necessity of $\eqref{eq:tractiff4}$.

%%%%%%%%%%%%%%%%%%%%%%%%%%

For $\varepsilon$ taking on all values in $(E(d),\infty)$, $i(\varepsilon,\vp)$ takes on (at least) all values 
\[
I_{d,\vp}:=\begin{cases} 
\emptyset, & i(E(d),\vp) = i(\infty,\vp) \\
\{i(\infty,\vp),\ldots, i(E(d),\vp)-1\}, & E(d) > 0, \\
\{i(\infty,\vp), i(\infty,\vp) + 1, \ldots\}, & E(d) = 0.
\end{cases}
\]
So,
\[
i\le  C_{\vp} T(\lambda_{i,d}^{-1},1,\vp)+1, \qquad \forall i\in I_{d,\vp},  \ d \in \naturals.
\]
This implies via our technical assumption \eqref{eq:ptauassume} that
\begin{gather}
\nonumber
 K_{\vp,\tau}\,T (\lambda_{i,d}^{-1},1,\tau \vp) \ge
 [T(\lambda_{i,d}^{-1},1, \vp)]^\tau
 \ge
  \left[\frac{(i-1)}{C_{\vp}}\right]^\tau \qquad i\in I_{d,\vp},  \ d \in \naturals, \\
  \label{eq:rest_strong_ineq}
 \frac{1}{T (\lambda_{i,d}^{-1},1,\tau \vp)} \le
\frac{K_{\vp,\tau}\, C_{\vp}^\tau}{(i-1)^\tau}\qquad \forall i \in I_{d,\vp} \setminus\{1\}, \ d \in \naturals .
\end{gather}

\item If $M(d) \ge L_{\tau\vp}$ and $E(d) = 0$, then $\{L_{\tau\vp},  \L_{\tau\vp} + 1, \ldots \} \subseteq I_{d,\vp} \setminus \{1\}$.

\end{enumerate}
Thus, in all three cases, the assumption of strong tractability on the restricted domain implies \eqref{eq:strong_rest_tractiff} with $\vp$ replaced by $\vp' = \tau \vp$, and so we see the necessity of $\eqref{eq:strong_rest_tractiff}$.
\bigskip

\noindent \textbf{Optimality:}
This proof is similar to the proof for the optimality condition for strong tractability in Theorem \ref{thm_main_strong_tract2}. We must show that $\cp_{\textup{trct}} = \widetilde{\cp}_{\textup{trct}}$.  Then, the expression for  $\cp_{\textup{opt}}$ in this theorem automatically follows from its definition in \eqref{eq:Poptdef}.

Furthermore, for all $d \in \naturals$, let $M(d) = \min \{n : \lambda_{n+1,d} \le E(d) \}$.  This means that 
\[
\lambda_{1,d}^{-1} \le \cdots \le \lambda_{M(d),d}^{-1} < E^{-1}(d) \le \lambda_{M(d)+1,d}^{-1}, \qquad (\lambda_{1,d}^{-1},d), \ldots, (\lambda_{M(d),d}^{-1},d) \in \Omega.
\]

>>>>

\begin{theorem}\label{thm_main_tract2}
Let $T$ be a tractability function as specified in \eqref{eq:Tspec} and satisfying \eqref{eq:Tconditions} and \eqref{eq:ptauassume}.  A problem is $T$-tractable iff there exists $\vp\ge \vzero$ and a positive constant $L_{\vp}$ such that
\begin{equation} \label{eq:tractiff4}
     S_{\vp}:=\sup_{d \in \naturals}
     \sum_{i = \lceil L_{\vp}\, T(0,d,\vp) \rceil}^\infty \frac{1}{T(\lambda^{-1}_{i,d},d,\vp)}< \infty.
\end{equation}

@@

\noindent \textbf{Optimality:} \\
This proof is similar to the proof for the optimality condition for strong tractability in Theorem \ref{thm_main_strong_tract2}. We must show that $\cp_{\textup{trct}} = \widetilde{\cp}_{\textup{trct}}$.  Then, the expression for  $\cp_{\textup{opt}}$ in this theorem automatically follows from its definition in \eqref{eq:Poptdef}.

@@

\begin{definition}
    A problem is strongly
$T$-tractable with parameter $\vp$ \emph{on the restricted domain $\Omega$} iff the complexity is independent of the dimension of the problem, that is, there exists a positive constant $C_{\vp}$, again independent of $\varepsilon$ and $d$, such that
\begin{equation} \label{eq:rest_strong_tract_def}
	\comp(\varepsilon,d) \le C_{\vp}\, T(\varepsilon^{-1},1,\vp) \qquad \forall(\varepsilon^{-1},d) \in \Omega.
\end{equation}
%\peter{[I am wondering whether this makes sense if $E$ depends on $d$? Do Gnewuch and Wo\'{z}niakowski allow dependence of $E$ on $d$?]}
A problem is 
$T$-tractable with parameter $\vp$ \emph{on the restricted domain $\Omega$} iff the complexity is independent of the dimension of the problem, that is, there exists a positive constant $C_{\vp}$, again independent of $\varepsilon$ and $d$, such that
\begin{equation} \label{eq:rest_tract_def}
	\comp(\varepsilon,d) \le C_{\vp}\, T(\varepsilon^{-1},d,\vp) \qquad \forall(\varepsilon^{-1},d) \in \Omega.
\end{equation}
 Define the closures of the sets of parameters for which our (strong) tractability conditions hold:
\begin{equation*}
	\cp_{\textup{rtrct}} : = \{\vp^* : \eqref{eq:rest_tract_def} \text{ holds }\forall \vp \in (\vp^*,\boldsymbol{\infty})\}, \qquad
	\cp_{\textup{rstrct}} : = \{\vp^* : \eqref{eq:rest_strong_tract_def} \text{ holds }\forall \vp \in (\vp^*,\boldsymbol{\infty})\}.
\end{equation*}
    The  set of optimal parameters is defined as all of those parameters satisfying the (strong) tractability conditions that are not greater than or equal to others:
\begin{gather}
	%\label{eq:rPoptdef}
	\mathcal{P}_{\textup{ropt}} : = \{\vp^* \in \cp_{\textup{rtrct}} :  \vp^* \notin [\vp,\boldsymbol{\infty}) \ \forall \vp \in  \cp_{\textup{rtrct}} \setminus \{\vp^*\} \}, \\
	%\label{eq:rPsoptdef}
	\mathcal{P}_{\textup{rsopt}} : = \{\vp^* \in \cp_{\textup{rstrct}} :  \vp^* \notin [\vp,\boldsymbol{\infty}) \ \forall \vp \in  \cp_{\textup{rstrct}} \setminus \{\vp^*\} \}.
\end{gather}
\end{definition}

@@

\item If $M(d) \ge L_{\tau\vp}$ and $E(d) = 0$, then $\{L_{\tau\vp},  L_{\tau\vp} + 1, \ldots \} \subseteq I_{d,\vp} \setminus \{1\}$.

@@

\bigskip
\noindent \textbf{Optimality:} \\ 
The proof of optimality is analogous to that for Theorem \ref{thm_main_strong_tract2} and is omitted.

@@

\begin{theorem}\label{thm_main_rest_tract}
Let $T$ be a tractability function as specified in \eqref{eq:Tspec} and satisfying \eqref{eq:Tconditions} and \eqref{eq:ptauassume}.  A problem is $T$-tractable on the restricted domain $\Omega$ iff there exists $\vp\ge \vzero$ and a positive constant $L_{\vp}$ such that
\begin{equation} \label{eq:rest_tractiff}
     S_{\vp}:=\sup_{d \in \naturals}
     \sum_{i = \lceil L_{\vp}\, T(0,d,\vp) \rceil}^{M(d)} \frac{1}{T(\lambda^{-1}_{i,d},d,\vp)}< \infty.
\end{equation}
If \eqref{eq:rest_tractiff} holds for some $\vp$, let $\widetilde{\cp}_{\textup{trct}} : = \{\vp^* : \eqref{eq:tractiff4} \text{ holds }\forall \vp \in (\vp^*,\boldsymbol{\infty}) \}$.
Then $\cp_{\textup{rtrct}} = \widetilde{\cp}_{\textup{rtrct}}$, and the set of optimal  tractability parameters is
\[
\cp_{\textup{ropt}} =
\{\vp^* \in \widetilde{\cp}_{\textup{rtrct}} :  \vp^* \notin [\widetilde{\vp},\boldsymbol{\infty}) \ \forall \widetilde{\vp}\in  \widetilde{\cp}_{\textup{rtrct}} \setminus \{\vp^*\} \}.
\]
\end{theorem}

@@

\noindent \textbf{Necessary condition:}\\
Suppose that we have
$T$-tractability on the restricted domain. That is, for some $\vp \ge \vzero$, there exists a positive constant $C_{\vp}$ such that
\[
\comp(\varepsilon,d)\le C_{\vp}\, T(\varepsilon^{-1},d,\vp) \qquad \forall (\varepsilon^{-1}, d) \in \Omega.
\]
Since the sequence of eigenvalues $\lambda_{1,d}, \lambda_{2,d}, \ldots $ is non-increasing, we have
\begin{equation}\label{eq:rest_lambda_K4}
	\lambda_{\lfloor C_{\vp}\, T(\varepsilon^{-1},d,\vp)\rfloor +1,d}\le \varepsilon \qquad 
 \forall \varepsilon > E(d),\ d \in \naturals.
\end{equation}

For $(\varepsilon^{-1}, d) \in \Omega$, define the positive integers 
\[
i (\varepsilon,d,\vp):= \lfloor C_{\vp}\, T(\varepsilon^{-1},d,\vp)\rfloor +1, \qquad
i (\infty,d,\vp) := \lfloor C_{\vp}\, T(0,d,\vp)\rfloor +1 \ge 1.
\]
It follows by \eqref{eq:rest_lambda_K4} that $\lambda_{i(\varepsilon,d,\vp),d} \le \varepsilon$
for any  $(\varepsilon^{-1}, d) \in \Omega$.
Note furthermore that since $T(\cdot,d,\vp)$ is non-decreasing, we have
\[
i(\varepsilon,d,\vp)\le C_{\vp}\, T(\varepsilon^{-1},d,\vp)+1 \le C_{\vp} T(\lambda_{i(\varepsilon,d,\vp),d}^{-1},d,\vp)+1, \qquad \forall \varepsilon > E(d),\ d \in \naturals.
\]
For $\varepsilon$ taking on all values in $(E(d),\infty)$, $i(\varepsilon,d,\vp)$ takes on (at least) all values in
\[
I_{d,\vp}:=\begin{cases} 
\emptyset, & i(E(d),d,\vp) = i(\infty,d,\vp), \\
\{i(\infty,d,\vp),\ldots, i(E(d),d,\vp)-1\}, & E(d) > 0, \\
\{i(\infty,d,\vp), i(\infty,d,\vp) + 1, \ldots\}, & E(d) = 0.
\end{cases}
\]
So,
\[
i\le  C_{\vp} T(\lambda_{i,d}^{-1},d,\vp)+1, \qquad \forall i\in I_{d},  \ d \in \naturals.
\]
This implies via our technical assumption \eqref{eq:ptauassume} that
\begin{gather}
\nonumber
 K_{\vp,\tau}\,T (\lambda_{i,d}^{-1},d,\tau \vp) \ge
 [T(\lambda_{i,d}^{-1},d, \vp)]^\tau
 \ge
  \left[\frac{(i-1)}{C_{\vp}}\right]^\tau \qquad i\in I_{d,\vp},  \ d \in \naturals, \\
  \label{eq:rest_ineq}
 \frac{1}{T (\lambda_{i,d}^{-1},d,\tau \vp)} \le
\frac{K_{\vp,\tau}\, C_{\vp}^\tau}{(i-1)^\tau}\qquad \forall i \in I_{d,\vp} \setminus\{1\}, \ d \in \naturals .
\end{gather}

To complete the proof, we will sum both sides of \eqref{eq:rest_ineq} over the range of $i$ appearing in \eqref{eq:rest_tractiff}, to establish that $S_{\vp'}$ is finite, where  $\vp' = \tau \vp$.  To do this we need to show that \eqref{eq:rest_ineq} holds for that range.

For any $d\in\naturals$, let
\begin{align*}
L_{\vp'} & := \left[C_{\vp'} + \frac{2}{T(0,1,\vp')}   \right]
\intertext{and note that }
 \min(i(\infty,d,\vp'),2) & \le i(\infty,d,\vp') +1  = \lfloor C_{\vp'}\, T(0,d,\vp')\rfloor +2 \le  \left[C_{\vp'} + \frac{2}{T(0,d,\vp')}   \right]\, T(0,d,\vp')\\
 & \le  L_{\vp'}\, T(0,d,\vp')
 \le \lceil L_{\vp'} T(0,d,\vp')\rceil .
\end{align*}
This is the inequality needed for the lower limit of the sum.

There are three cases.
\begin{enumerate}
\renewcommand{\labelenumi}{\roman{enumi})}

\item If $M(d) <\lceil L_{\vp'} T(0,d,\vp')\rceil$, then 
\[
\sum_{i = \lceil L_{\vp'} T(0,d,\vp')\rceil }^{M(d)} \frac{1}{T (\lambda_{i,d}^{-1},1, \vp')} = 0,
\]
which does not affect the finiteness of $S_{\vp'}$.

\item If $M(d) \ge \lceil L_{\vp'} T(0,d,\vp')\rceil$ and $E(d) = 0$, then $\{\lceil L_{\vp'} T(0,d,\vp')\rceil,  \lceil L_{\vp'} T(0,d,\vp')\rceil + 1, \ldots \} \subseteq I_{d,\vp} \setminus \{1\}$.

\item If $M(d) \ge \lceil L_{\vp'} T(0,d,\vp')\rceil$ and $E(d) >0$, then \eqref{eq:Mddef} and \eqref{eq:rest_lambda_K4} imply that
\[
\lambda_{i(E(d),d,\vp),d} \le \lambda_{M(d)+1,d} \le E(d) < \lambda_{M(d),d}.
\]
This means that $M(d) \le i(E(d),d,\vp)-1$.  So, $\{ \lceil L_{\vp'} T(0,d,\vp')\rceil, \ldots, M(d)\} \subseteq I_{d,\vp} \setminus \{1\}$.

In both the second and third cases,
\begin{align*}
S_{\vp'} & = \sup_{d\in\naturals} \sum_{i =  \lceil L_{\vp'} T(0,d,\vp')\rceil}^{M(d)} \frac{1}{T (\lambda_{i,d}^{-1},d, \tau \vp)}
\le 
\sup_{d\in\naturals} \sum_{i \in I_{d,\vp} \setminus\{1\} } \frac{1}{T (\lambda_{i,d}^{-1},1, \tau \vp)} \\
&  \le  K_{\vp,\tau}\, C_{\vp}^\tau
\sum_{i=2}^\infty \frac{1}{(i-1)^\tau}
 \le K_{\vp,\tau}\, C_{\vp}^\tau
\zeta (\tau) 
 < \infty \qquad \text{by \eqref{eq:rest_strong_ineq},}
\end{align*}
where $\zeta$ denotes the Riemann zeta function.

\end{enumerate}
Thus, in all three cases, the assumption of strong tractability on the restricted domain implies \eqref{eq:rest_tractiff} with $\vp$ replaced by $\vp' = \tau \vp$, and so we see the necessity of $\eqref{eq:rest_tractiff}$.
\bigskip

\noindent \textbf{Optimality:} \\
The proof of optimality is analogous to that for Theorem \ref{thm_main_tract2} and is omitted.

\noindent 
This concludes the proof of Theorem \ref{thm_main_tract2}.
\end{proof}

\fred{Are there cases that we can discuss where we do not have (strong) tractability, but we do have (strong) tractability on a restricted domain, such as $(0,\infty) \times \{1, \ldots, d_{\max}] \cup (\varepsilon_{\min}^{-1},\infty) \times \naturals$}
